Model Checking Differentially Private Properties

### 2018-06-12 above-threshold.tex
explain actions and add them to the figure.

      (t'1r'0) edge [double] node [above]
              { \hide{$0|0, 0|1$} } (t'1r0)
      (t'1r'0) edge [double] node [above] 
              { \hide{$1|0, 1|1, 1|2$} } (t'1r1)
      (t'1r'0) edge [double] node [below] 
              { \hide{$2|1, 2|2$} } (t'1r2)

@@

      (tt'2rr'0) edge [double] node [above] 
                 { \hide{$0|0, 1|0$} } (tt'2rr0)
      (tt'2rr'0) edge [double] node [above] 
                 { \hide{$0|1, 1|1, 2|1$} } (tt'2rr1)
      (tt'2rr'0) edge [double] node [above] 
                 { \hide{$1|2, 2|2$} } (tt'2rr2)

      (tt'2rr'1) edge [double] node [above]
                { \hide{$0|0, 1|0$} } (tt'2rr0)
      (tt'2rr'1) edge [double] node [above]
                { \hide{$0|1, 1|1, 2|1$} } (tt'2rr1)
      (tt'2rr'1) edge [double] node [above]
                { \hide{$1|2, 2|2$} } (tt'2rr2)

@@

Now, the non-deterministic choices in the two computation cannot be 
independent. Recall that the sensitivity of each query is
$1$. If the top computation moves to the state, say, $t'_1r_0$, it
means the next query result on the dataset is $0$. Subsequently, the
bottom computation can only move to $\underline{t}'_j\underline{r}_0$
or $\underline{t}'_j\underline{r}_1$ depending on its perturbed
threshold. This is where actions are useful. Define the actions
$\{ m\underline{n} : |m - n| \leq 1 \}$. The action
$m\underline{n}$ represents that the next query result for the dataset
and its neighbor are $m$ and $n$ respectively. For instance, the
non-deterministic choice from $t'_1r'_0$ to $t'_1r_0$ is associated
with two actions $0\underline{0}$ and $0\underline{1}$ (but not
$0\underline{2}$). Similarly, the choice from
$\underline{t}'_2\underline{r}'_1$ to
$\underline{t}'_2\underline{r}_0$ is associated with the actions
$0\underline{0}$ and $1\underline{0}$ (but not $2\underline{0}$). On
the action $0\underline{0}$, the top computation moves to $t'_ir_0$ and
the bottom computation moves to $\underline{t}'_j\underline{r}_0$ by
their respective perturbed thresholds.
Actions make sure the two computation of neighbors
is modeled properly. It remains to define the neighborhood
relation. Recall the sensitivity is $1$. Consider the neighborhood
relation 
$\{ (t_ir_m, t_ir_m),
    (\underline{t}_i\underline{r}_n, \underline{t}_i\underline{r}_n),
    (t_ir_m, \underline{t}_i\underline{r}_n), 
    (\underline{t}_i\underline{r}_n, t_ir_m) : | m - n | \leq 1 \}$.
That is, two states are neighbors if they represent two inputs of the
same threshold and query results with difference at most one.

>>>>

      (t'1r'0) edge [double] node [right]
              { \rotatebox{270}{$0\underline{0}, 0\underline{1}$} } (t'1r0)
      (t'1r'0) edge [double] node [right=-8] 
              { \rotatebox{315}{$1\underline{0}, 
                                 1\underline{1}, 1\underline{2}$} } (t'1r1)
      (t'1r'0) edge [double] node [right] 
              { \rotatebox{334}{$2\underline{1}, 2\underline{2}$} } (t'1r2)

@@

      (tt'2rr'0) edge [double] node [right] 
                 { \rotatebox{270}{$0\underline{0}, 1\underline{0}$} } (tt'2rr0)
      (tt'2rr'0) edge [double] node [above] 
                 { \hide{$0|1, 1|1, 2|1$} } (tt'2rr1)
      (tt'2rr'0) edge [double] node [above] 
                 { \hide{$1|2, 2|2$} } (tt'2rr2)

      (tt'2rr'1) edge [double] node [right=15,below=-11]
                { \rotatebox{315}{$0\underline{0}, 1\underline{0}$} } (tt'2rr0)
      (tt'2rr'1) edge [double] node [above]
                { \hide{$0|1, 1|1, 2|1$} } (tt'2rr1)
      (tt'2rr'1) edge [double] node [above]
                { \hide{$1|2, 2|2$} } (tt'2rr2)

@@

Now, the non-deterministic choices in the two computation cannot be 
independent. Recall that the sensitivity of each query is
$1$. If the top computation moves to the state, say, $t'_1r_0$, it
means the next query result on the dataset is $0$. Subsequently, the
bottom computation can only move to $\underline{t}'_j\underline{r}_0$
or $\underline{t}'_j\underline{r}_1$ depending on its perturbed
threshold. This is where actions are useful. Define the actions
$\{ m\underline{n} : |m - n| \leq 1 \}$. The action
$m\underline{n}$ represents that the next query result for the dataset
and its neighbor are $m$ and $n$ respectively. For instance, the
non-deterministic choice from $t'_1r'_0$ to $t'_1r_0$ is associated
with two actions $0\underline{0}$ and $0\underline{1}$ (but not
$0\underline{2}$). Similarly, the choice from
$\underline{t}'_2\underline{r}'_1$ to
$\underline{t}'_2\underline{r}_0$ is associated with the actions
$0\underline{0}$ and $1\underline{0}$ (but not $2\underline{0}$). 
Assume the perturbed thresholds of the top and bottom computation are
$i$ and $j$ respectively. On the action $0\underline{0}$, the top
computation moves to $t'_ir_0$ and 
the bottom computation moves to $\underline{t}'_j\underline{r}_0$ 
Actions make sure the two computation of neighbors
is modeled properly. Now consider the action sequence
$-,-,0\underline{1},-,2\underline{2},-,2\underline{1}$ from the states
$t_0r_1$ and $\underline{t}_0\underline{r}_0$ (``$-$'' represents the
purely probabilistic action). Together with the first query results, 
it denotes four consecutive query results $1$, $0$, $2$, $2$ on the
top computation, and $0$, $1$, $2$, $1$ on the bottom computation.
Each action sequence models two sequences of query results: one on the
top, the other on the bottom computation. Moreover, the difference of
the corresponding query results on the two computation is at most one
by the definition of the action set. Any sequence of adaptive query
results is hence formalized by an action sequence in our model.

It remains to define the neighborhood
relation. Recall the sensitivity is $1$. Consider the neighborhood
relation 
$\{ (t_ir_m, t_ir_m),
    (\underline{t}_i\underline{r}_n, \underline{t}_i\underline{r}_n),
    (t_ir_m, \underline{t}_i\underline{r}_n), 
    (\underline{t}_i\underline{r}_n, t_ir_m) : | m - n | \leq 1 \}$.
That is, two states are neighbors if they represent two inputs of the
same threshold and query results with difference at most one.
